Leveraging the VTA-TVM Hardware-Software Stack \\for FPGA Acceleration of 8-bit ResNet-18 Inference

### 2018-06-13 dissemination.publication/9375838469ad4029/paper.tex
final pass

\paragraph{Single Kernel Evaluation}
We then evaluate each layer individually to evaluate TVM's ability to efficiently utilize the accelerator's resources.
The results are shown in the Roofline diagram in Figure ~\ref{fig:fpga_latencyhiding}.
Roofline performance diagrams provide insight on how well computation and memory resources are utilized on a given system for different workloads.
Overall, virtual threading in TVM improves performance on all ResNet layers by exploiting latency hiding mechanisms in VTA's decoupled access-execute pipeline.
Peak compute utilization increases from 70\% with no virtual threading to 88\% with virtual threading turned on (to hide memory access latency).

@@

\begin{verbatim}

$ ck install package:lib-tvm-runtime-master --env.PACKAGE_GIT_CHECKOUT=e4c2af9abdcb3c7aabafba8084414d7739c17c4c

  choose Python 3!

$ ck run program:vta-pynq-server --sudo

  during first execution other missing soft dependencies 
  will be detected or installed including libdma.so and VTA server.

\end{verbatim}

@@

\begin{verbatim}
$ ck install package:lib-tvm-master-cpu --env.PACKAGE_GIT_CHECKOUT=e4c2af9abdcb3c7aabafba8084414d7739c17c4c
 Select Python 2.x
 LLVM > 4.x

$ ck install package:lib-nnvm-master --env.PACKAGE_URL=https://github.com/tqchen/nnvm \
    --env.PACKAGE_GIT_CHECKOUT=qt

$ ck install package:lib-vta-python-master
\end{verbatim}

>>>>

\paragraph{Single Kernel Evaluation}
We evaluate each layer individually to evaluate TVM's ability to efficiently utilize the accelerator's resources.
The results are shown in the Roofline diagram in Figure ~\ref{fig:fpga_latencyhiding}.
Roofline performance diagrams provide insight on how well computation and memory resources are utilized on a given system for different workloads.
Overall, virtual threading in TVM improves performance on all ResNet layers by exploiting latency hiding mechanisms in VTA's decoupled access-execute pipeline.
Peak compute utilization increases from 70\% with no virtual threading to 88\% with virtual threading turned on (to hide memory access latency).

@@

\begin{verbatim}
$ ck install package:lib-tvm-runtime-master --env.PACKAGE_GIT_CHECKOUT=e4c2af9abdcb3c7aabafba8084414d7739c17c4c
\end{verbatim}

Choose Python 3!

\begin{verbatim}
$ ck run program:vta-pynq-server --sudo
\end{verbatim}

During first execution other missing soft dependencies 
will be detected or installed including libdma.so and VTA server.

@@

\begin{verbatim}
$ ck install package:lib-tvm-master-cpu --env.PACKAGE_GIT_CHECKOUT=e4c2af9abdcb3c7aabafba8084414d7739c17c4c
\end{verbatim}

Select Python 2.x and LLVM > 4.x

\begin{verbatim}
$ ck install package:lib-nnvm-master --env.PACKAGE_URL=https://github.com/tqchen/nnvm \
    --env.PACKAGE_GIT_CHECKOUT=qt
$ ck install package:lib-vta-python-master
\end{verbatim}
